FoRTE baseline

### 2019-04-30 analysis/paper/paper.Rmd
[paper] Fix within vs across caption bug
[paper] Minor cleanup of outline

## Structural uncertainty details

- Understory light environment and how it affects species matters
- The multiple-scatter
    - Fig: RTM comparison (Radiation profile)
    - Fig: Crown model comparison
    - Fig: Trait plasticity?

@@

@@

`r mdcap within_vs_across_cap`

@@

## Structural uncertainty

```{r rad_prof, fig.cap = rad_barplot_cap, fig.dim = c(5, 7)}
rad_barplot_cap <- paste(
  "Comparison of radiation profiles under two-stream and multiple scatter",
  "canopy radiative transfer models."
)
readd(rad_lineplot)
```

@@

Compared to the default two-stream model, the multiple scatter model leads to slightly less beam (direct) radiation in the understory but slightly more diffuse radiation.

>>>>

@@

`r mdcap(within_vs_across_cap)`

@@

@@

## Details about model structures

```{r rad_prof, fig.cap = rad_barplot_cap, fig.dim = c(5, 7)}
rad_barplot_cap <- paste(
  "Comparison of radiation profiles under two-stream and multiple scatter",
  "canopy radiative transfer models."
)
```

@@

<!-- Compared to the default two-stream model, the multiple scatter model leads to slightly less beam (direct) radiation in the understory but slightly more diffuse radiation. -->

(TODO)
